nospace_10000

### 2021-10-14 graphs_newt_snakes/nospce_10000.Rmd
I was writing what I was seeing in the space simulations when they are run for a long time. I am also looked at the dirstibtuion for space simulation results for 3000 gen.

>>>>

No space to 10,000 generations works, but space simulation does not one of the populations seems to die out before it reaches the end of the simulation. I wonder how to stop this from happening? maybe a function that makes it harder for them to find each other when the population is low. Under 2 seems to have run to completion. Now I am trying an under 2 msprime and a under 5 mutation rate (success). Maybe the file i was using was bad trying under 5 10000 gens again (does not work, still dies out).

 Are the newts and snake coevolving? - it's difficult to tell. I can see patterns forming (certain phenotypes are clustering), but the mean phenotype doesn't move. But the distributions (at least for under 5) look different.

 When I run the simulation for longer the phenotype of newts and snakes get large around 3000 -population size might be a consequence of a large phenotype. (looking at the distributions soon)

 paste0("End Space: Generation", end_gen)
